---
title: "Averaging intensity by time point- Negative AUs"
output: html_notebook
---


1. Average intensity for each negative AU per test trial (angry, fearful, neutral, happy) per time point (all participants)
2. Average intensity for mean negative AU per test trial per time bin (all participants)

__________________________________________________________________________________________
Clear environment
```{r}
remove(list = ls())
```

Set working directory
```{r}
setwd("~/MATLAB")
```

Load packages
```{r load-packages, message = FALSE}
library(tidyverse)
library(readxl)
library(jtools)
```

Load data
```{r}
angry_trials <- read_excel("MASTER Affectiva angry trial neg AUs.xlsx")
fear_trials <- read_excel("MASTER Affectiva fearful trial neg AUs.xlsx")
neutral_trials <- read_excel("MASTER Affectiva neutral trial neg AUs.xlsx")
happy_trials <- read_excel("MASTER Affectiva happy trial neg AUs.xlsx")
```

____________________________________________________________________________________
## 1. Average intensity for each negative AU per test trial (angry, fearful, neutral, happy) per time point (all participants)

Angry, Fearful, Happy, Neutral (all participants)
Averaging each AU at each time point per trial
```{r}
angry_trials <- round(angry_trials, 3)
fear_trials <- round(fear_trials, 3)
happy_trials <- round(happy_trials, 3)
neutral_trials <- round(neutral_trials, 3)

#angry_trials <- as.numeric(angry_trials)
#fear_trials <- as.numeric(fear_trials)
#happy_trials <- as.numeric(happy_trials)
#neutral_trials <- as.numeric(neutral_trials)

average_angry_trials_all <- angry_trials %>%
      dplyr::group_by(Standardized_time) %>%
      dplyr::summarise(meanIBR = mean(inner_brow_raise),
                meanBR = mean(brow_raise), 
                meanBF = mean(brow_furrow), 
                meanNW = mean(nose_wrinkle),
                meanULR = mean(upper_lip_raise),
                meanLCD = mean(lip_corner_depressor),
                meanCR = mean(chin_raise),
                meanLS = mean(lip_stretch), 
                meanLP = mean(lip_press)
                )

average_fear_trials_all <- fear_trials %>%
      dplyr::group_by(Standardized_time) %>%
      dplyr::summarise(meanIBR = mean(inner_brow_raise),
                meanBR = mean(brow_raise), 
                meanBF = mean(brow_furrow), 
                meanNW = mean(nose_wrinkle),
                meanULR = mean(upper_lip_raise),
                meanLCD = mean(lip_corner_depressor),
                meanCR = mean(chin_raise),
                meanLS = mean(lip_stretch), 
                meanLP = mean(lip_press)
                )

average_happy_trials_all <- happy_trials %>%
      dplyr::group_by(Standardized_time) %>%
      dplyr::summarise(meanIBR = mean(inner_brow_raise),
                meanBR = mean(brow_raise), 
                meanBF = mean(brow_furrow), 
                meanNW = mean(nose_wrinkle),
                meanULR = mean(upper_lip_raise),
                meanLCD = mean(lip_corner_depressor),
                meanCR = mean(chin_raise),
                meanLS = mean(lip_stretch), 
                meanLP = mean(lip_press)
                )

average_neutral_trials_all <- neutral_trials %>%
      dplyr::group_by(Standardized_time) %>%
      dplyr::summarise(meanIBR = mean(inner_brow_raise),
                meanBR = mean(brow_raise), 
                meanBF = mean(brow_furrow), 
                meanNW = mean(nose_wrinkle),
                meanULR = mean(upper_lip_raise),
                meanLCD = mean(lip_corner_depressor),
                meanCR = mean(chin_raise),
                meanLS = mean(lip_stretch), 
                meanLP = mean(lip_press)
                )

```

__________________________________________________________________________________________
## 2. Average intensity for grand mean AU per test trial per time bin (all participants) - CSV file output for SPSS and plot

Adding a column for trial ("Angry", "Fear", etc.) and a column for bin (bin 1 = 0 - 10 seconds, bin 2 = 10.001 - 20 seconds)
```{r}

average_angry_trials_all$Trial <- "angry"
average_fear_trials_all$Trial <- "fear"
average_happy_trials_all$Trial <- "happy"
average_neutral_trials_all$Trial <- "neutral"
      
#Angry
average_angry_trials_all$Bin[average_angry_trials_all$Standardized_time < 10.001] <- 1
average_angry_trials_all$Bin[average_angry_trials_all$Standardized_time >= 10.001] <- 2

average_angry_trials_all <- dplyr::mutate(average_angry_trials_all, grandMean = rowMeans(select(average_angry_trials_all, starts_with("mean")), na.rm = TRUE))

average_angry_trials_allS <- average_angry_trials_all %>%
      select(Standardized_time, Trial, Bin, grandMean)

#Fear 
average_fear_trials_all$Bin[average_fear_trials_all$Standardized_time < 10.001] <- 1
average_fear_trials_all$Bin[average_fear_trials_all$Standardized_time >= 10.001] <- 2

average_fear_trials_all <- dplyr::mutate(average_fear_trials_all, grandMean = rowMeans(select(average_fear_trials_all, starts_with("mean")), na.rm = TRUE))

average_fear_trials_allS <- average_fear_trials_all %>%
      select(Standardized_time, Trial, Bin, grandMean)

#Happy
average_happy_trials_all$Bin[average_happy_trials_all$Standardized_time < 10.001] <- 1
average_happy_trials_all$Bin[average_happy_trials_all$Standardized_time >= 10.001] <- 2

average_happy_trials_all <- dplyr::mutate(average_happy_trials_all, grandMean = rowMeans(select(average_happy_trials_all, starts_with("mean")), na.rm = TRUE))

average_happy_trials_allS <- average_happy_trials_all %>%
      select(Standardized_time, Trial, Bin, grandMean)

#Neutral
average_neutral_trials_all$Bin[average_neutral_trials_all$Standardized_time < 10.001] <- 1
average_neutral_trials_all$Bin[average_neutral_trials_all$Standardized_time >= 10.001] <- 2

average_neutral_trials_all <- dplyr::mutate(average_neutral_trials_all, grandMean = rowMeans(select(average_neutral_trials_all, starts_with("mean")), na.rm = TRUE))

average_neutral_trials_allS <- average_neutral_trials_all %>%
      select(Standardized_time, Trial, Bin, grandMean)

#Put all trials in 1 df
avgGrandMean_perTimePoint_perTrialS <- rbind(average_angry_trials_allS, average_neutral_trials_allS, average_fear_trials_allS, average_happy_trials_allS)

#Wide format
avgGrandMean_perTimePoint_perTrialSW <- avgGrandMean_perTimePoint_perTrialS %>%
      spread(Trial, grandMean)


##write csv
write.csv(avgGrandMean_perTimePoint_perTrialSW, file = "avgGrandMeans.csv")
```

```{r}
ggplot(data = avgGrandMean_perTimePoint_perTrialS, aes(x = Standardized_time, y = grandMean, color = Trial)) +
      geom_line()
```

## average per 5 seconds - for data reduction purposes


```{r}
avgGrandMean_perTimePoint_perTrialS$FiveSecIncrmts[avgGrandMean_perTimePoint_perTrialS$Standardized_time < 5.001] <- 1

avgGrandMean_perTimePoint_perTrialS$FiveSecIncrmts[(avgGrandMean_perTimePoint_perTrialS$Standardized_time >= 5.001) & (avgGrandMean_perTimePoint_perTrialS$Standardized_time < 10.001)] <- 2

avgGrandMean_perTimePoint_perTrialS$FiveSecIncrmts[(avgGrandMean_perTimePoint_perTrialS$Standardized_time >= 10.001) & (avgGrandMean_perTimePoint_perTrialS$Standardized_time < 15.001)] <- 3

avgGrandMean_perTimePoint_perTrialS$FiveSecIncrmts[avgGrandMean_perTimePoint_perTrialS$Standardized_time >= 15.001] <- 4

avgGrandMean_perTimePoint_perTrialSW_5sec <- avgGrandMean_perTimePoint_perTrialS %>%
      spread(Trial, grandMean)


##write csv
write.csv(avgGrandMean_perTimePoint_perTrialSW_5sec, file = "avgGrandMeans_5sec.csv")

averageGrandMean_perTimePoint_perTrialS_4graph <- avgGrandMean_perTimePoint_perTrialS %>%
      dplyr::group_by(FiveSecIncrmts, Trial) %>%
      dplyr::summarise(meanGrandMean = mean(grandMean))

```

## need to make graph for 5 sec one

```{r}
ggplot(data = averageGrandMean_perTimePoint_perTrialS_4graph, aes(x = factor(FiveSecIncrmts), y = meanGrandMean, color = Trial)) +
      geom_point(aes(size = .25)) +
      xlab("Time Bin") +
  ylab("Grand Mean Intensity - Negative AUs") +
  theme_apa(legend.pos = "right", legend.use.title = FALSE,
  legend.font.size = 10, x.font.size = 12, y.font.size = 12,
  facet.title.size = 10, remove.y.gridlines = TRUE,
  remove.x.gridlines = TRUE) +
  theme(legend.key.size = unit(0.5, "cm"),
  legend.key.width = unit(0.5,"cm"))
```

```{r}
ggplot(data = averageGrandMean_perTimePoint_perTrialS_4graph, aes(x = FiveSecIncrmts, y = meanGrandMean, color = Trial)) +
      geom_point() +
      geom_line() +
      xlab("Time Bin") +
  ylab("Grand Mean Intensity") +
  theme_apa(legend.pos = "right", legend.use.title = FALSE,
  legend.font.size = 10, x.font.size = 12, y.font.size = 12,
  facet.title.size = 10, remove.y.gridlines = TRUE,
  remove.x.gridlines = TRUE) +
  theme(legend.key.size = unit(0.5, "cm"),
  legend.key.width = unit(0.5,"cm"))
```


Average of each AU per trial for bin 1 and bin 2
```{r}
average_angry_trials_all1 <- average_angry_trials_all %>%
      filter(Bin == 1) %>%
      summarise(meanIBR_bin = mean(meanIBR),
                meanBR_bin = mean(meanBR), 
                meanBF_bin = mean(meanBF), 
                meanNW_bin = mean(meanNW),
                meanULR_bin = mean(meanULR),
                meanLCD_bin = mean(meanLCD),
                meanCR_bin = mean(meanCR),
                meanLS_bin = mean(meanLS), 
                meanLP_bin = mean(meanLP)
                )
      
average_angry_trials_all2 <- average_angry_trials_all %>%
      filter(Bin == 2) %>%
      summarise(meanIBR_bin = mean(meanIBR),
                meanBR_bin = mean(meanBR), 
                meanBF_bin = mean(meanBF), 
                meanNW_bin = mean(meanNW),
                meanULR_bin = mean(meanULR),
                meanLCD_bin = mean(meanLCD),
                meanCR_bin = mean(meanCR),
                meanLS_bin = mean(meanLS), 
                meanLP_bin = mean(meanLP)
                )

average_fear_trials_all1 <- average_fear_trials_all %>%
      filter(Bin == 1) %>%
      summarise(meanIBR_bin = mean(meanIBR),
                meanBR_bin = mean(meanBR), 
                meanBF_bin = mean(meanBF), 
                meanNW_bin = mean(meanNW),
                meanULR_bin = mean(meanULR),
                meanLCD_bin = mean(meanLCD),
                meanCR_bin = mean(meanCR),
                meanLS_bin = mean(meanLS), 
                meanLP_bin = mean(meanLP)
                )
      
average_fear_trials_all2 <- average_fear_trials_all %>%
      filter(Bin == 2) %>%
      summarise(meanIBR_bin = mean(meanIBR),
                meanBR_bin = mean(meanBR), 
                meanBF_bin = mean(meanBF), 
                meanNW_bin = mean(meanNW),
                meanULR_bin = mean(meanULR),
                meanLCD_bin = mean(meanLCD),
                meanCR_bin = mean(meanCR),
                meanLS_bin = mean(meanLS), 
                meanLP_bin = mean(meanLP)
                )

average_happy_trials_all1 <- average_happy_trials_all %>%
      filter(Bin == 1) %>%
      summarise(meanIBR_bin = mean(meanIBR),
                meanBR_bin = mean(meanBR), 
                meanBF_bin = mean(meanBF), 
                meanNW_bin = mean(meanNW),
                meanULR_bin = mean(meanULR),
                meanLCD_bin = mean(meanLCD),
                meanCR_bin = mean(meanCR),
                meanLS_bin = mean(meanLS), 
                meanLP_bin = mean(meanLP)
                )
      
average_happy_trials_all2 <- average_happy_trials_all %>%
      filter(Bin == 2) %>%
      summarise(meanIBR_bin = mean(meanIBR),
                meanBR_bin = mean(meanBR), 
                meanBF_bin = mean(meanBF), 
                meanNW_bin = mean(meanNW),
                meanULR_bin = mean(meanULR),
                meanLCD_bin = mean(meanLCD),
                meanCR_bin = mean(meanCR),
                meanLS_bin = mean(meanLS), 
                meanLP_bin = mean(meanLP)
                )

average_neutral_trials_all1 <- average_neutral_trials_all %>%
      filter(Bin == 1) %>%
      summarise(meanIBR_bin = mean(meanIBR),
                meanBR_bin = mean(meanBR), 
                meanBF_bin = mean(meanBF), 
                meanNW_bin = mean(meanNW),
                meanULR_bin = mean(meanULR),
                meanLCD_bin = mean(meanLCD),
                meanCR_bin = mean(meanCR),
                meanLS_bin = mean(meanLS), 
                meanLP_bin = mean(meanLP)
                )
      
average_neutral_trials_all2 <- average_neutral_trials_all %>%
      filter(Bin == 2) %>%
      summarise(meanIBR_bin = mean(meanIBR),
                meanBR_bin = mean(meanBR), 
                meanBF_bin = mean(meanBF), 
                meanNW_bin = mean(meanNW),
                meanULR_bin = mean(meanULR),
                meanLCD_bin = mean(meanLCD),
                meanCR_bin = mean(meanCR),
                meanLS_bin = mean(meanLS), 
                meanLP_bin = mean(meanLP)
                )

```

Putting the averages of both bins into one dataframe
```{r}
average_angry_per_bin <- rbind(average_angry_trials_all1, average_angry_trials_all2)
average_angry_per_bin$Trial <- "angry"
average_angry_per_bin$Bin <- c(1,2)


average_fear_per_bin <- rbind(average_fear_trials_all1, average_fear_trials_all2)
average_fear_per_bin$Trial <- "fear"
average_fear_per_bin$Bin <- c(1,2)


average_happy_per_bin <- rbind(average_happy_trials_all1, average_happy_trials_all2)
average_happy_per_bin$Trial <- "happy"
average_happy_per_bin$Bin <- c(1,2)

average_neutral_per_bin <- rbind(average_neutral_trials_all1, average_neutral_trials_all2)
average_neutral_per_bin$Trial <- "neutral"
average_neutral_per_bin$Bin <- c(1,2)


average_all_per_bin <- rbind(average_angry_per_bin, average_neutral_per_bin, average_happy_per_bin, average_fear_per_bin)
```


Reshaping data (long)
```{r}
average_all_per_bin_long <- average_all_per_bin %>%
      gather(AU, avg_Intensity, meanIBR_bin:meanLP_bin)

```


```{r}
ggplot(data = average_all_per_bin_long, aes(x = factor(Bin), y = avg_Intensity, color = AU)) +
      geom_point() +
      facet_grid(cols = vars(Trial)) +
      ggtitle("Average intensity for negative AUs by time bin")

```
_________________________________________________________________________________________

## 3. Grand negative AU means per test trial


```{r}
grand_negAU_means <- average_all_per_bin %>%
      group_by(Trial,Bin) %>%
      summarise(grandMean = mean(meanIBR_bin:meanLP_bin))


ggplot(data = grand_negAU_means, aes(x = factor(Bin), y = grandMean, color = Trial)) +
      geom_point() 

```