---
title: "Averaging intensity by time point- Positive AU"
output: html_notebook
---


1. Average intensity for mean positive AU per test trial per time bin (all participants)

__________________________________________________________________________________________
Clear environment
```{r}
remove(list = ls())
```

Set working directory
```{r}
setwd("~/MATLAB")
```

Load packages
```{r load-packages, message = FALSE}
library(tidyverse)
library(readxl)
library(jtools)
```

Load data
```{r}
angry_trials <- read_excel("MASTER Affectiva angry trial pos AU.xlsx")
fear_trials <- read_excel("MASTER Affectiva fearful trial pos AU.xlsx")
neutral_trials <- read_excel("MASTER Affectiva neutral trial pos AU.xlsx")
happy_trials <- read_excel("MASTER Affectiva happy trial pos AU.xlsx")
```

____________________________________________________________________________________
## 1. Average intensity for each positive AU per test trial (angry, fearful, neutral, happy) per time point (all participants)

Angry, Fearful, Happy, Neutral (all participants)
Averaging each AU at each time point per trial
```{r}
angry_trials <- round(angry_trials, 3)
fear_trials <- round(fear_trials, 3)
happy_trials <- round(happy_trials, 3)
neutral_trials <- round(neutral_trials, 3)


angry_trials <- angry_trials %>%
      dplyr::group_by(Standardized_time) %>%
      dplyr::summarise(meanCR = mean(cheek_raise))

fear_trials <- fear_trials %>%
      dplyr::group_by(Standardized_time) %>%
      dplyr::summarise(meanCR = mean(cheek_raise))

happy_trials <- happy_trials %>%
      dplyr::group_by(Standardized_time) %>%
      dplyr::summarise(meanCR = mean(cheek_raise))

neutral_trials <- neutral_trials %>%
      dplyr::group_by(Standardized_time) %>%
      dplyr::summarise(meanCR = mean(cheek_raise))
```

__________________________________________________________________________________________
## 2. Average intensity for grand mean AU per test trial per time bin (all participants) - CSV file output for SPSS and plot

Adding a column for trial ("Angry", "Fear", etc.) and a column for bin (bin 1 = 0 - 10 seconds, bin 2 = 10.001 - 20 seconds)
```{r}

angry_trials$Trial <- "angry"
fear_trials$Trial <- "fear"
happy_trials$Trial <- "happy"
neutral_trials$Trial <- "neutral"
      
#Angry
angry_trials$Bin[angry_trials$Standardized_time < 10.001] <- 1
angry_trials$Bin[angry_trials$Standardized_time >= 10.001] <- 2

angry_trials$grandMean <- angry_trials$meanCR

angry_trialsS <- angry_trials %>%
      select(Standardized_time, Trial, Bin, grandMean)

#Fear 
fear_trials$Bin[fear_trials$Standardized_time < 10.001] <- 1
fear_trials$Bin[fear_trials$Standardized_time >= 10.001] <- 2

fear_trials$grandMean <- fear_trials$meanCR

fear_trialsS <- fear_trials %>%
      select(Standardized_time, Trial, Bin, grandMean)

#Happy
happy_trials$Bin[happy_trials$Standardized_time < 10.001] <- 1
happy_trials$Bin[happy_trials$Standardized_time >= 10.001] <- 2

happy_trials$grandMean <- happy_trials$meanCR

happy_trialsS <- happy_trials %>%
      select(Standardized_time, Trial, Bin, grandMean)

#Neutral
neutral_trials$Bin[neutral_trials$Standardized_time < 10.001] <- 1
neutral_trials$Bin[neutral_trials$Standardized_time >= 10.001] <- 2

neutral_trials$grandMean <- neutral_trials$meanCR

neutral_trialsS <- neutral_trials %>%
      select(Standardized_time, Trial, Bin, grandMean)

#Put all trials in 1 df
avgGrandMean_perTimePoint_perTrialS_pos <- rbind(angry_trialsS, neutral_trialsS, fear_trialsS, happy_trialsS)

#Wide format
avgGrandMean_perTimePoint_perTrialSW_pos <- avgGrandMean_perTimePoint_perTrialS_pos %>%
      spread(Trial, grandMean)


##write csv
write.csv(avgGrandMean_perTimePoint_perTrialSW_pos, file = "avgGrandMeans_POS.csv")
```


```{r}
ggplot(data = avgGrandMean_perTimePoint_perTrialS_pos, aes(x = Standardized_time, y = grandMean, color = Trial)) +
      geom_line()
```

## average per 5 seconds - for data reduction purposes


```{r}
avgGrandMean_perTimePoint_perTrialS_pos$FiveSecIncrmts[avgGrandMean_perTimePoint_perTrialS_pos$Standardized_time < 5.001] <- 1

avgGrandMean_perTimePoint_perTrialS_pos$FiveSecIncrmts[(avgGrandMean_perTimePoint_perTrialS_pos$Standardized_time >= 5.001) & (avgGrandMean_perTimePoint_perTrialS_pos$Standardized_time < 10.001)] <- 2

avgGrandMean_perTimePoint_perTrialS_pos$FiveSecIncrmts[(avgGrandMean_perTimePoint_perTrialS_pos$Standardized_time >= 10.001) & (avgGrandMean_perTimePoint_perTrialS_pos$Standardized_time < 15.001)] <- 3

avgGrandMean_perTimePoint_perTrialS_pos$FiveSecIncrmts[avgGrandMean_perTimePoint_perTrialS_pos$Standardized_time >= 15.001] <- 4

avgGrandMean_perTimePoint_perTrialSW_5sec_pos <- avgGrandMean_perTimePoint_perTrialS_pos %>%
      spread(Trial, grandMean)


##write csv
write.csv(avgGrandMean_perTimePoint_perTrialSW_5sec_pos, file = "avgGrandMeans_5sec_POS.csv")

```

## need to make graph for 5 sec one

```{r}

averageGrandMean_perTimePoint_perTrialS_4graph_pos <- avgGrandMean_perTimePoint_perTrialS_pos %>%
      dplyr::group_by(FiveSecIncrmts, Trial) %>%
      dplyr::summarise(meanGrandMean = mean(grandMean))


ggplot(data = averageGrandMean_perTimePoint_perTrialS_4graph_pos, aes(x = FiveSecIncrmts, y = meanGrandMean, color = Trial)) +
      geom_point() +
      geom_line() +
      xlab("Time Bin") +
  ylab("Grand Mean Intensity") +
  theme_apa(legend.pos = "right", legend.use.title = FALSE,
  legend.font.size = 10, x.font.size = 12, y.font.size = 12,
  facet.title.size = 10, remove.y.gridlines = TRUE,
  remove.x.gridlines = TRUE) +
  theme(legend.key.size = unit(0.5, "cm"),
  legend.key.width = unit(0.5,"cm"))
```









Average of each AU per trial for bin 1 and bin 2
```{r}
angry_trials1 <- angry_trials %>%
      filter(Bin == 1) %>%
      summarise(meanIBR_bin = mean(meanIBR),
                meanBR_bin = mean(meanBR), 
                meanBF_bin = mean(meanBF), 
                meanNW_bin = mean(meanNW),
                meanULR_bin = mean(meanULR),
                meanLCD_bin = mean(meanLCD),
                meanCR_bin = mean(meanCR),
                meanLS_bin = mean(meanLS), 
                meanLP_bin = mean(meanLP)
                )
      
angry_trials2 <- angry_trials %>%
      filter(Bin == 2) %>%
      summarise(meanIBR_bin = mean(meanIBR),
                meanBR_bin = mean(meanBR), 
                meanBF_bin = mean(meanBF), 
                meanNW_bin = mean(meanNW),
                meanULR_bin = mean(meanULR),
                meanLCD_bin = mean(meanLCD),
                meanCR_bin = mean(meanCR),
                meanLS_bin = mean(meanLS), 
                meanLP_bin = mean(meanLP)
                )

fear_trials1 <- fear_trials %>%
      filter(Bin == 1) %>%
      summarise(meanIBR_bin = mean(meanIBR),
                meanBR_bin = mean(meanBR), 
                meanBF_bin = mean(meanBF), 
                meanNW_bin = mean(meanNW),
                meanULR_bin = mean(meanULR),
                meanLCD_bin = mean(meanLCD),
                meanCR_bin = mean(meanCR),
                meanLS_bin = mean(meanLS), 
                meanLP_bin = mean(meanLP)
                )
      
fear_trials2 <- fear_trials %>%
      filter(Bin == 2) %>%
      summarise(meanIBR_bin = mean(meanIBR),
                meanBR_bin = mean(meanBR), 
                meanBF_bin = mean(meanBF), 
                meanNW_bin = mean(meanNW),
                meanULR_bin = mean(meanULR),
                meanLCD_bin = mean(meanLCD),
                meanCR_bin = mean(meanCR),
                meanLS_bin = mean(meanLS), 
                meanLP_bin = mean(meanLP)
                )

happy_trials1 <- happy_trials %>%
      filter(Bin == 1) %>%
      summarise(meanIBR_bin = mean(meanIBR),
                meanBR_bin = mean(meanBR), 
                meanBF_bin = mean(meanBF), 
                meanNW_bin = mean(meanNW),
                meanULR_bin = mean(meanULR),
                meanLCD_bin = mean(meanLCD),
                meanCR_bin = mean(meanCR),
                meanLS_bin = mean(meanLS), 
                meanLP_bin = mean(meanLP)
                )
      
happy_trials2 <- happy_trials %>%
      filter(Bin == 2) %>%
      summarise(meanIBR_bin = mean(meanIBR),
                meanBR_bin = mean(meanBR), 
                meanBF_bin = mean(meanBF), 
                meanNW_bin = mean(meanNW),
                meanULR_bin = mean(meanULR),
                meanLCD_bin = mean(meanLCD),
                meanCR_bin = mean(meanCR),
                meanLS_bin = mean(meanLS), 
                meanLP_bin = mean(meanLP)
                )

neutral_trials1 <- neutral_trials %>%
      filter(Bin == 1) %>%
      summarise(meanIBR_bin = mean(meanIBR),
                meanBR_bin = mean(meanBR), 
                meanBF_bin = mean(meanBF), 
                meanNW_bin = mean(meanNW),
                meanULR_bin = mean(meanULR),
                meanLCD_bin = mean(meanLCD),
                meanCR_bin = mean(meanCR),
                meanLS_bin = mean(meanLS), 
                meanLP_bin = mean(meanLP)
                )
      
neutral_trials2 <- neutral_trials %>%
      filter(Bin == 2) %>%
      summarise(meanIBR_bin = mean(meanIBR),
                meanBR_bin = mean(meanBR), 
                meanBF_bin = mean(meanBF), 
                meanNW_bin = mean(meanNW),
                meanULR_bin = mean(meanULR),
                meanLCD_bin = mean(meanLCD),
                meanCR_bin = mean(meanCR),
                meanLS_bin = mean(meanLS), 
                meanLP_bin = mean(meanLP)
                )

```

Putting the averages of both bins into one dataframe
```{r}
average_angry_per_bin <- rbind(angry_trials1, angry_trials2)
average_angry_per_bin$Trial <- "angry"
average_angry_per_bin$Bin <- c(1,2)


average_fear_per_bin <- rbind(fear_trials1, fear_trials2)
average_fear_per_bin$Trial <- "fear"
average_fear_per_bin$Bin <- c(1,2)


average_happy_per_bin <- rbind(happy_trials1, happy_trials2)
average_happy_per_bin$Trial <- "happy"
average_happy_per_bin$Bin <- c(1,2)

average_neutral_per_bin <- rbind(neutral_trials1, neutral_trials2)
average_neutral_per_bin$Trial <- "neutral"
average_neutral_per_bin$Bin <- c(1,2)


average_all_per_bin <- rbind(average_angry_per_bin, average_neutral_per_bin, average_happy_per_bin, average_fear_per_bin)
```


Reshaping data (long)
```{r}
average_all_per_bin_long <- average_all_per_bin %>%
      gather(AU, avg_Intensity, meanIBR_bin:meanLP_bin)

```


```{r}
ggplot(data = average_all_per_bin_long, aes(x = factor(Bin), y = avg_Intensity, color = AU)) +
      geom_point() +
      facet_grid(cols = vars(Trial)) +
      ggtitle("Average intensity for negative AUs by time bin")

```

_________________________________________________________________________________________

## 3. Grand negative AU means per test trial


```{r}
grand_negAU_means <- average_all_per_bin %>%
      group_by(Trial,Bin) %>%
      summarise(grandMean = mean(meanIBR_bin:meanLP_bin))


ggplot(data = grand_negAU_means, aes(x = factor(Bin), y = grandMean, color = Trial)) +
      geom_point() 

```









