---
title: "Data exploration EPAR"
output: html_notebook
---

*Kate Dixon - 2019*

1. General graphs/data viz (line 42)
2. Percentage of look time per expression pair based on crawling status (line 73)
3. One-sample T-test (mean proportion of look time vs. chance (.50)) for crawlers and non-crawlers (line 106)
4. Percentage of look time per expression pair based on abbreviated EE questionnaire (line 228)
5. One-sample T-test (mean proportion of look time vs. chance (.50)) for high vs. low scores on      abbreviated EE questionnaire (line 273)
6. Percentage of look time per expression pair based on full EE questionnaire (line 371)
7. One-sample T-test (mean proportion of look time vs. chance (.50)) for high vs. low scores on full EE questionnaire (line 420)
8. Two-Way ANOVA 2x2- (EE abreviated scores: high, low), (Crawling stats: non-crawler, crawler), on percentage look time to each pair (line 520)
9. Is age significantly different between high/low or non-crawler/crawler groups?
10. MANOVA - 2 MANOVAs, one per group (Crawlers and Non-crawlers), with Abbreviated High/Low EE scores as a between-subjects factor and the proportion scores for each pair as the DVs (6) (line 600)
11. Wilcoxon (independent samples)- Crawlers and non-crawlers assesed separately, high vs. low on each preference score for pair
12. Wilcoxon one sample


-MANOVA
-age? ANCOVA?
-using block 1 instead of total
-crawler & high EE, crawler & low EE also NC & high and NC and low- ANOVA
-outliers?
-siblings (Y/N) different btw groups?



Set WD
```{r}
setwd("~/MATLAB")
```

Libraries
```{r}
library(readxl)
library(formattable)
library('tidyverse')
library(car)
```

Getting data
```{r}
EPAR_full <- read_excel("MASTER EPAR 8.1.19.xlsx")
```

___________________________________________________________________________________________________
## 1. General graphs/data viz

Scatterplot of individual participants' proportions of look time to angry face in AH pair
Color based on whether or not individual is crawling
Dashed line is at 0.50 
```{r}
ggplot(EPAR_full, aes(x = Part_ID, y = perctA_AH, color = CrawlingYN)) +
  geom_point() +
  geom_hline(yintercept = 0.5, linetype = "dashed", size = 0.5)
  
```

Scatterplot of individual participants' proportions of look time to angry face in AH pair and
score on certain questions of the EE questionnaire
Color based on whether or not individual is crawling
Dashed line is at 0.50 
```{r}
ggplot(EPAR_full, aes(x = SumQ1_2_5_11_12_13, y = perctA_AH, color = CrawlingYN)) +
  geom_point() +
  geom_hline(yintercept = 0.5, linetype = "dashed", size = 0.5)
  
```

Boxplot - Looking time to happy face in AH pair by crawling status
```{r}
ggplot(EPAR_full, aes(x = factor(CrawlingYN), y = perctH_AH, fill = factor(CrawlingYN))) +
  geom_boxplot()
```

_____________________________________________________________________________________________________

## 2. Percentage of look time per expression pair based on crawling status

Mean percentage of look time per facial expression pair for each crawling group
```{r}
EPAR_full[!is.na(EPAR_full),]
avg_percts <- EPAR_full %>%
  select(CrawlingYN, perctH_AH, perctA_AN, perctF_FA, perctF_HF, perctN_HN, perctF_NF) %>%
  group_by(CrawlingYN) %>%
  summarize(mean_perctH_AH = mean(perctH_AH, na.rm = TRUE),
            mean_perctA_AN = mean(perctA_AN, na.rm = TRUE),
            mean_perctF_FA = mean(perctF_FA, na.rm = TRUE),
            mean_perctF_HF = mean(perctF_HF, na.rm = TRUE),
            mean_perctN_HN = mean(perctN_HN, na.rm = TRUE),
            mean_perctF_NF = mean (perctF_NF, na.rm = TRUE))
avg_percts
```


Reshaping the above table for graphing purposes
```{r}
means_EPAR <- avg_percts %>% 
  gather(Pair, Percentage, mean_perctH_AH:mean_perctF_NF)
means_EPAR
```

Bar graph of percentage of total look time to certain face in each expression pair based on crawling status
```{r}
ggplot(means_EPAR, aes(x = factor(Pair), y = Percentage, fill = factor(CrawlingYN))) +
  geom_bar(position = "dodge", stat = "identity") +
  coord_cartesian(ylim = c(0.3, 0.7)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", size = 0.5)
```

_____________________________________________________________________________________________________
## 3. One-sample T-test (mean proportion of look time vs. chance (.50)) for crawlers and non-crawlers 

Shapiro-Wilk test for normality (can assume normality if not significant) & Q-Q plots
```{r}
shapiro.test(EPAR_full$perctA_AH)
shapiro.test(EPAR_full$perctA_AN)
shapiro.test(EPAR_full$perctF_FA)
shapiro.test(EPAR_full$perctF_HF)
shapiro.test(EPAR_full$perctN_HN)
shapiro.test(EPAR_full$perctF_NF)

ggplot(EPAR_full, aes(sample = perctA_AH)) +
  stat_qq() +
  stat_qq_line()

ggplot(EPAR_full, aes(sample = perctA_AN)) +
  stat_qq() +
  stat_qq_line()
```

Splitting main dataframe into crawlers and non-crawlers
```{r}
crawlers <- EPAR_full %>% 
  filter(CrawlingYN == 1)

non_crawlers <- EPAR_full %>%
  filter(CrawlingYN == 0)
```


One-sample t-tests for crawlers (one-sample Wilcoxon signed rank test for when data is not normally distributed)
```{r}
resultA_AH_C <- t.test(crawlers$perctA_AH, mu = 0.50)
resultA_AN_C <- t.test(crawlers$perctA_AN, mu = 0.50)
resultF_FA_C <- t.test(crawlers$perctF_FA, mu = 0.50)
resultF_HF_C <- t.test(crawlers$perctF_HF, mu = 0.50)
resultN_HN_C <- t.test(crawlers$perctN_HN, mu = 0.50)
resultF_NF_C <- t.test(crawlers$perctF_NF, mu = 0.50)

resultA_AH_C
resultA_AN_C
resultF_FA_C
resultF_HF_C
resultN_HN_C
resultF_NF_C

resultA_AH_Cwil <- wilcox.test(crawlers$perctA_AH, mu = 0.50)
```

Bar graph for crawlers (have to change where asterisks are based on above significance)
```{r}
avg_percts_C <- crawlers %>%
  select(perctH_AH, perctA_AN, perctF_FA, perctF_HF, perctN_HN, perctF_NF) %>%
  summarize(mean_perctH_AHC = mean(perctH_AH, na.rm = TRUE),
            mean_perctA_ANC = mean(perctA_AN, na.rm = TRUE),
            mean_perctF_FAC = mean(perctF_FA, na.rm = TRUE),
            mean_perctF_HFC = mean(perctF_HF, na.rm = TRUE),
            mean_perctN_HNC = mean(perctN_HN, na.rm = TRUE),
            mean_perctF_NFC = mean (perctF_NF, na.rm = TRUE))

means_crawlers <- avg_percts_C %>% 
  gather(Pair, Percentage, mean_perctH_AHC:mean_perctF_NFC)

asterisks <- data.frame(Pair = c("mean_perctF_FAC", "mean_perctN_HNC", "mean_perctF_NFC"),
                        Percentage = c(.63, .48, .60))

C_bar <- ggplot(means_crawlers, aes(x = factor(Pair), y = Percentage)) +
  geom_bar(position = "dodge", stat = "identity") +
  coord_cartesian(ylim = c(0.3, 0.7)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", size = 0.5) +
  geom_text(data = asterisks, label = "*", size = 10)
C_bar
```


One-sample t-tests for non-crawlers
```{r}
resultA_AH_NC <- t.test(non_crawlers$perctA_AH, mu = 0.50)
resultA_AN_NC <- t.test(non_crawlers$perctA_AN, mu = 0.50)
resultF_FA_NC <- t.test(non_crawlers$perctF_FA, mu = 0.50)
resultF_HF_NC <- t.test(non_crawlers$perctF_HF, mu = 0.50)
resultN_HN_NC <- t.test(non_crawlers$perctN_HN, mu = 0.50)
resultF_NF_NC <- t.test(non_crawlers$perctF_NF, mu = 0.50)

resultA_AH_NC
resultA_AN_NC
resultF_FA_NC
resultF_HF_NC
resultN_HN_NC
resultF_NF_NC

resultA_AH_NCwil <- wilcox.test(non_crawlers$perctA_AH, mu = 0.50)

```

Bargraph for non-crawlers (have to change coordinates for asterisks based on significance)
```{r}
avg_percts_NC <- non_crawlers %>%
  select(perctH_AH, perctA_AN, perctF_FA, perctF_HF, perctN_HN, perctF_NF) %>%
  summarize(mean_perctH_AHNC = mean(perctH_AH, na.rm = TRUE),
            mean_perctA_ANNC = mean(perctA_AN, na.rm = TRUE),
            mean_perctF_FANC = mean(perctF_FA, na.rm = TRUE),
            mean_perctF_HFNC = mean(perctF_HF, na.rm = TRUE),
            mean_perctN_HNNC = mean(perctN_HN, na.rm = TRUE),
            mean_perctF_NFNC = mean (perctF_NF, na.rm = TRUE))

means_non_crawlers <- avg_percts_NC %>% 
  gather(Pair, Percentage, mean_perctH_AHNC:mean_perctF_NFNC)

asterisks2 <- data.frame(Pair = c("mean_perctF_FANC", "mean_perctF_HFNC"),
                        Percentage = c(.63, .63))

NCbar <- ggplot(means_non_crawlers, aes(x = factor(Pair), y = Percentage)) +
  geom_bar(position = "dodge", stat = "identity") +
  coord_cartesian(ylim = c(0.3, 0.7)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", size = 0.5) +
  geom_text(data = asterisks2, label = "*", size = 10)
NCbar
```

______________________________________________________________________________________________

## 4. Percentage of look time per expression pair based on abbreviated EE questionnaire

New variable based on score from certain questions on the EE questionnaire (#1,2,5,11,12,13)- new variable is a median split of high/low scores
```{r}
medianEEsum <- median(EPAR_full$SumQ1_2_5_11_12_13)
EPAR_full$HighLowEEscore[EPAR_full$SumQ1_2_5_11_12_13 >= medianEEsum] <- 'high'
EPAR_full$HighLowEEscore[EPAR_full$SumQ1_2_5_11_12_13 < medianEEsum] <- 'low'

```

Mean percentage of look time per facial expression pair for high and low EE questionnaire group (the abreviated EE questionnaire, see above)
```{r}
highlow_percts <- EPAR_full %>%
  select(HighLowEEscore, perctH_AH, perctA_AN, perctF_FA, perctF_HF, perctN_HN, perctF_NF) %>%
  group_by(HighLowEEscore) %>%
  summarize(mean_perctH_AH = mean(perctH_AH, na.rm = TRUE),
            mean_perctA_AN = mean(perctA_AN, na.rm = TRUE),
            mean_perctF_FA = mean(perctF_FA, na.rm = TRUE),
            mean_perctF_HF = mean(perctF_HF, na.rm = TRUE),
            mean_perctN_HN = mean(perctN_HN, na.rm = TRUE),
            mean_perctF_NF = mean (perctF_NF, na.rm = TRUE))
highlow_percts
```

Reshaping above dataframe
```{r}
means_EPARHL <- highlow_percts %>% 
  gather(Pair, Percentage, mean_perctH_AH:mean_perctF_NF)
means_EPARHL
```

Bar graph of percentage of total look time to certain face in each expression pair based on scores for certain questions on the EE questionnaire (high/low)
```{r}
ggplot(means_EPARHL, aes(x = factor(Pair), y = Percentage, fill = factor(HighLowEEscore))) +
  geom_bar(position = "dodge", stat = "identity") +
  coord_cartesian(ylim = c(0.3, 0.7)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", size = 0.5)
```

Boxplot - Looking time to happy face in AH pair by abbreviated EE score
```{r}
ggplot(EPAR_full, aes(x = factor(HighLowEEscore), y = perctH_AH, fill = factor(HighLowEEscore))) +
  geom_boxplot()
```

__________________________________________________________________________________________________
## 5. One-sample T-test (mean proportion of look time vs. chance (.50)) for high vs. low scores on abbreviated EE questionnaire

Splitting main dataframe into high/low scores
```{r}
highEE <- EPAR_full %>% 
  filter(HighLowEEscore == "high")

lowEE <- EPAR_full %>%
  filter(HighLowEEscore == "low")
```

One-sample t-tests for highEE
```{r}
resultA_AH_high <- t.test(highEE$perctA_AH, mu = 0.50)
resultA_AN_high <- t.test(highEE$perctA_AN, mu = 0.50)
resultF_FA_high <- t.test(highEE$perctF_FA, mu = 0.50)
resultF_HF_high <- t.test(highEE$perctF_HF, mu = 0.50)
resultN_HN_high <- t.test(highEE$perctN_HN, mu = 0.50)
resultF_NF_high <- t.test(highEE$perctF_NF, mu = 0.50)

resultA_AH_high
resultA_AN_high
resultF_FA_high
resultF_HF_high
resultN_HN_high
resultF_NF_high

```

Bargraph for high EE (abbreviated) (have to change coordinates for asterisks based on significance)
```{r}
avg_percts_highEE <- highEE %>%
  select(perctH_AH, perctA_AN, perctF_FA, perctF_HF, perctN_HN, perctF_NF) %>%
  summarize(mean_perctH_AH_highEE = mean(perctH_AH, na.rm = TRUE),
            mean_perctA_AN_highEE = mean(perctA_AN, na.rm = TRUE),
            mean_perctF_FA_highEE = mean(perctF_FA, na.rm = TRUE),
            mean_perctF_HF_highEE = mean(perctF_HF, na.rm = TRUE),
            mean_perctN_HN_highEE = mean(perctN_HN, na.rm = TRUE),
            mean_perctF_NF_highEE = mean (perctF_NF, na.rm = TRUE))

means_highEE <- avg_percts_highEE %>% 
  gather(Pair, Percentage, mean_perctH_AH_highEE:mean_perctF_NF_highEE)

asterisks <- data.frame(Pair = c("mean_perctF_FA_highEE","mean_perctF_NF_highEE"),
                        Percentage = c(.65, .60))

highEE_bar <- ggplot(means_highEE, aes(x = factor(Pair), y = Percentage)) +
  geom_bar(position = "dodge", stat = "identity") +
  coord_cartesian(ylim = c(0.3, 0.7)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", size = 0.5) +
  geom_text(data = asterisks, label = "*", size = 10)
highEE_bar
```

One-sample t-tests for lowEE
```{r}
resultA_AH_low <- t.test(lowEE$perctA_AH, mu = 0.50)
resultA_AN_low <- t.test(lowEE$perctA_AN, mu = 0.50)
resultF_FA_low <- t.test(lowEE$perctF_FA, mu = 0.50)
resultF_HF_low <- t.test(lowEE$perctF_HF, mu = 0.50)
resultN_HN_low <- t.test(lowEE$perctN_HN, mu = 0.50)
resultF_NF_low <- t.test(lowEE$perctF_NF, mu = 0.50)

resultA_AH_low
resultA_AN_low
resultF_FA_low
resultF_HF_low
resultN_HN_low 
resultF_NF_low


```

Bargraph for low EE (abbreviated) (have to change coordinates for asterisks based on significance)
```{r}
avg_percts_lowEE <- lowEE %>%
  select(perctH_AH, perctA_AN, perctF_FA, perctF_HF, perctN_HN, perctF_NF) %>%
  summarize(mean_perctH_AH_lowEE = mean(perctH_AH, na.rm = TRUE),
            mean_perctA_AN_lowEE = mean(perctA_AN, na.rm = TRUE),
            mean_perctF_FA_lowEE = mean(perctF_FA, na.rm = TRUE),
            mean_perctF_HF_lowEE = mean(perctF_HF, na.rm = TRUE),
            mean_perctN_HN_lowEE = mean(perctN_HN, na.rm = TRUE),
            mean_perctF_NF_lowEE = mean(perctF_NF, na.rm = TRUE))

means_lowEE <- avg_percts_lowEE %>% 
  gather(Pair, Percentage, mean_perctH_AH_lowEE:mean_perctF_NF_lowEE)

asterisks <- data.frame(Pair = c("mean_perctF_HF_lowEE", "mean_perctN_HN_lowEE"),
                        Percentage = c(.62, .46))

lowEE_bar <- ggplot(means_lowEE, aes(x = factor(Pair), y = Percentage)) +
  geom_bar(position = "dodge", stat = "identity") +
  coord_cartesian(ylim = c(0.3, 0.7)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", size = 0.5) +
  geom_text(data = asterisks, label = "*", size = 10)
lowEE_bar
```

_____________________________________________________________________________________________
## 6. Percentage of look time per expression pair based on full EE questionnaire

New variable based on total sum of EE questionnaire
```{r}
EPAR_full$Total_EEscore <- rowSums(EPAR_full[, 605:617])
```

New variable based on total score from EE questionnaire- new variable is a median split of high/low scores
```{r}
medianEEtotal <- median(EPAR_full$Total_EEscore)
EPAR_full$HighLowEEscore2[EPAR_full$Total_EEscore >= medianEEtotal] <- 'high'
EPAR_full$HighLowEEscore2[EPAR_full$Total_EEscore < medianEEtotal] <- 'low'
```

Mean percentage of look time per facial expression pair for high and low EE questionnaire group (the full EE questionnaire, see above)
```{r}
highlow_perctsTotal <- EPAR_full %>%
  select(HighLowEEscore2, perctH_AH, perctA_AN, perctF_FA, perctF_HF, perctN_HN, perctF_NF) %>%
  group_by(HighLowEEscore2) %>%
  summarize(mean_perctH_AH_total = mean(perctH_AH, na.rm = TRUE),
            mean_perctA_AN_total = mean(perctA_AN, na.rm = TRUE),
            mean_perctF_FA_total = mean(perctF_FA, na.rm = TRUE),
            mean_perctF_HF_total = mean(perctF_HF, na.rm = TRUE),
            mean_perctN_HN_total = mean(perctN_HN, na.rm = TRUE),
            mean_perctF_NF_total = mean (perctF_NF, na.rm = TRUE))
highlow_perctsTotal
```

Reshaping above dataframe
```{r}
means_EPARHL_total <- highlow_perctsTotal %>% 
  gather(Pair, Percentage, mean_perctH_AH_total:mean_perctF_NF_total)
means_EPARHL_total
```

Bar graph of percentage of total look time to certain face in each expression pair based on total scores for the EE questionnaire (high/low)
```{r}
ggplot(means_EPARHL_total, aes(x = factor(Pair), y = Percentage, fill = factor(HighLowEEscore2))) +
  geom_bar(position = "dodge", stat = "identity") +
  coord_cartesian(ylim = c(0.3, 0.7)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", size = 0.5)
```

Boxplot - Looking time to happy face in AH pair by total EE score
```{r}
ggplot(EPAR_full, aes(x = factor(HighLowEEscore2), y = perctH_AH, fill = factor(HighLowEEscore2))) +
  geom_boxplot()
```

___________________________________________________________________________________________________
## 7. One-sample T-test (mean proportion of look time vs. chance (.50)) for high vs. low scores on full EE questionnaire

Splitting main dataframe into high/low scores
```{r}
highEE2 <- EPAR_full %>% 
  filter(HighLowEEscore2 == "high")

lowEE2 <- EPAR_full %>%
  filter(HighLowEEscore2 == "low")
```


One-sample t-tests for highEE2
```{r}
resultA_AH_high2 <- t.test(highEE2$perctA_AH, mu = 0.50)
resultA_AN_high2 <- t.test(highEE2$perctA_AN, mu = 0.50)
resultF_FA_high2 <- t.test(highEE2$perctF_FA, mu = 0.50)
resultF_HF_high2 <- t.test(highEE2$perctF_HF, mu = 0.50)
resultN_HN_high2 <- t.test(highEE2$perctN_HN, mu = 0.50)
resultF_NF_high2 <- t.test(highEE2$perctF_NF, mu = 0.50)

resultA_AH_high2
resultA_AN_high2
resultF_FA_high2
resultF_HF_high2
resultN_HN_high2
resultF_NF_high2

```

Bargraph for high EE (full) (have to change coordinates for asterisks based on significance)
```{r}
avg_percts_highEE2 <- highEE2 %>%
  select(perctH_AH, perctA_AN, perctF_FA, perctF_HF, perctN_HN, perctF_NF) %>%
  summarize(mean_perctH_AH_highEE2 = mean(perctH_AH, na.rm = TRUE),
            mean_perctA_AN_highEE2 = mean(perctA_AN, na.rm = TRUE),
            mean_perctF_FA_highEE2 = mean(perctF_FA, na.rm = TRUE),
            mean_perctF_HF_highEE2 = mean(perctF_HF, na.rm = TRUE),
            mean_perctN_HN_highEE2 = mean(perctN_HN, na.rm = TRUE),
            mean_perctF_NF_highEE2 = mean (perctF_NF, na.rm = TRUE))

means_highEE2 <- avg_percts_highEE2 %>% 
  gather(Pair, Percentage, mean_perctH_AH_highEE2:mean_perctF_NF_highEE2)

asterisks <- data.frame(Pair = c("mean_perctF_FA_highEE2"),
                        Percentage = c(.63))

highEE2_bar <- ggplot(means_highEE2, aes(x = factor(Pair), y = Percentage)) +
  geom_bar(position = "dodge", stat = "identity") +
  coord_cartesian(ylim = c(0.3, 0.7)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", size = 0.5) +
  geom_text(data = asterisks, label = "*", size = 10)
highEE2_bar
```

One-sample t-tests for lowEE2
```{r}
resultA_AH_low2 <- t.test(lowEE2$perctA_AH, mu = 0.50)
resultA_AN_low2 <- t.test(lowEE2$perctA_AN, mu = 0.50)
resultF_FA_low2 <- t.test(lowEE2$perctF_FA, mu = 0.50)
resultF_HF_low2 <- t.test(lowEE2$perctF_HF, mu = 0.50)
resultN_HN_low2 <- t.test(lowEE2$perctN_HN, mu = 0.50)
resultF_NF_low2 <- t.test(lowEE2$perctF_NF, mu = 0.50)

resultA_AH_low2
resultA_AN_low2
resultF_FA_low2
resultF_HF_low2
resultN_HN_low2
resultF_NF_low2


```


Bargraph for low EE (full) (have to change coordinates for asterisks based on significance)
```{r}
avg_percts_lowEE2 <- lowEE2 %>%
  select(perctH_AH, perctA_AN, perctF_FA, perctF_HF, perctN_HN, perctF_NF) %>%
  summarize(mean_perctH_AH_lowEE2 = mean(perctH_AH, na.rm = TRUE),
            mean_perctA_AN_lowEE2 = mean(perctA_AN, na.rm = TRUE),
            mean_perctF_FA_lowEE2 = mean(perctF_FA, na.rm = TRUE),
            mean_perctF_HF_lowEE2 = mean(perctF_HF, na.rm = TRUE),
            mean_perctN_HN_lowEE2 = mean(perctN_HN, na.rm = TRUE),
            mean_perctF_NF_lowEE2 = mean(perctF_NF, na.rm = TRUE))

means_lowEE2 <- avg_percts_lowEE2 %>% 
  gather(Pair, Percentage, mean_perctH_AH_lowEE2:mean_perctF_NF_lowEE2)

asterisks <- data.frame(Pair = c("mean_perctN_HN_lowEE2"),
                        Percentage = c(.46))

lowEE_bar <- ggplot(means_lowEE, aes(x = factor(Pair), y = Percentage)) +
  geom_bar(position = "dodge", stat = "identity") +
  coord_cartesian(ylim = c(0.3, 0.7)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", size = 0.5) +
  geom_text(data = asterisks, label = "*", size = 10)
lowEE_bar
```

______________________________________________________________________________________________________
## 8. Two-Way ANOVA 2x2- (EE abreviated scores: high, low), (Crawling stats: non-crawler, crawler), on percentage look time to each pair

Grab only needed variables
```{r}
EPAR4ANOVA <- EPAR_full %>%
  select(CrawlingYN, HighLowEEscore, perctH_AH)
```


Check structure to see how R is reading the variables (need the independent variables to be factors)
```{r}
str(EPAR4ANOVA)
```

Convert variables to factors and recode the levels
```{r}
EPAR4ANOVA$CrawlingYN <- factor(EPAR4ANOVA$CrawlingYN,
                                levels = c(0, 1),
                                labels = c("non_crawler", "crawler"))

EPAR4ANOVA$HighLowEEscore <- factor(EPAR4ANOVA$HighLowEEscore,
                                levels = c("high", "low"),
                                labels = c("high", "low"))


str(EPAR4ANOVA)
```

Frequency table (to see how many participants are in each cell)- balanced or unbalanced?
```{r}
table(EPAR4ANOVA$CrawlingYN, EPAR4ANOVA$HighLowEEscore)
```

Visualize data
```{r}
ggplot(EPAR4ANOVA, aes(x = CrawlingYN, y = perctH_AH, fill = HighLowEEscore)) +
  geom_boxplot()
```

Compute two-way ANOVA- Does look time to happy in AH pair depend on crawling status and abbreviated EE score? 
```{r}
library(car)
result_aov <- aov(perctH_AH ~ CrawlingYN * HighLowEEscore, data = EPAR4ANOVA)
Anova(result_aov, type = "III")
```

Compute mean and SD by groups
```{r}
group_by(EPAR4ANOVA, CrawlingYN, HighLowEEscore) %>%
  summarise(
    count = n(),
    mean = mean(perctH_AH, na.rm = TRUE),
    sd = sd(perctH_AH, na.rm = TRUE)
  )
```

Levene's Test for homogeneity of variance (isn't significant = no evidence to suggest that the variance across groups is statistically significantly different, can assume homogeneity)
```{r}
leveneTest(perctH_AH ~ CrawlingYN*HighLowEEscore, data = EPAR4ANOVA)
```

____________________________________________________________________________________________________
## 9. Is age different between groups? (do I need to do an MANOVA or a MANCOVA?)
```{r}
Age_lowhigh <- EPAR_full %>%
  select(HighLowEEscore, Age_in_mos)

res <- t.test(Age_in_mos ~ HighLowEEscore, data = Age_lowhigh, var.equal = TRUE)
res

Age_CNC <- EPAR_full %>%
  select(CrawlingYN, Age_in_mos)

res2 <- t.test(Age_in_mos ~ CrawlingYN, data = Age_CNC, var.equal = TRUE)
res2
```
___________________________________________________________________________________________________
## 10.MANOVAs - 2 MANOVAs, one per group (Crawlers and Non-crawlers), with Abbreviated High/Low EE scores as a between-subjects factor and the proportion scores for each pair as the DVs (6)
```{r}

EPAR4MANOVA <- EPAR_full %>%
  select(CrawlingYN, HighLowEEscore, perctH_AH, perctA_AN, perctF_FA, perctF_HF, perctN_HN, perctF_NF )
str(EPAR4MANOVA)


EPAR4MANOVA$HighLowEEscore <- factor(EPAR4ANOVA$HighLowEEscore,
                                levels = c("high", "low"),
                                labels = c("high", "low"))


str(EPAR4MANOVA)

crawlersMANOVA <- EPAR4MANOVA %>% 
  filter(CrawlingYN == 1)

non_crawlersMANOVA <- EPAR4MANOVA %>%
  filter(CrawlingYN == 0)

results_CMANOVA <- manova(cbind(perctH_AH, perctA_AN, perctF_FA, perctF_HF, perctN_HN, perctF_NF) ~ HighLowEEscore, data = crawlersMANOVA)

results_NCMANOVA <- manova(cbind(perctH_AH, perctA_AN, perctF_FA, perctF_HF, perctN_HN, perctF_NF) ~ HighLowEEscore, data = non_crawlersMANOVA)

summary(results_CMANOVA)
summary(results_NCMANOVA)

```



```{r}
crawlbyhighlow <- EPAR4MANOVA %>%
  select(HighLowEEscore, CrawlingYN, perctH_AH, perctA_AN, perctF_FA, perctF_HF, perctN_HN, perctF_NF) %>%
  group_by(CrawlingYN, HighLowEEscore) %>%
  summarize(mean_perctH_AH3 = mean(perctH_AH, na.rm = TRUE),
            mean_perctA_AN3 = mean(perctA_AN, na.rm = TRUE),
            mean_perctF_FA3 = mean(perctF_FA, na.rm = TRUE),
            mean_perctF_HF3 = mean(perctF_HF, na.rm = TRUE),
            mean_perctN_HN3 = mean(perctN_HN, na.rm = TRUE),
            mean_perctF_NF3 = mean (perctF_NF, na.rm = TRUE))

crawlbyhighlow


```

```{r}
means_crawlbyhighlow <- crawlbyhighlow %>% 
  gather(Pair, Percentage, mean_perctH_AH3:mean_perctF_NF3)
means_crawlbyhighlow
```


```{r}
ggplot(means_crawlbyhighlow, aes(x = factor(Pair), y = Percentage, fill = factor(HighLowEEscore))) +
  geom_bar(position = "dodge", stat = "identity") +
  coord_cartesian(ylim = c(0.3, 0.7)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", size = 0.5) +
  facet_grid(.~CrawlingYN)
```
__________________________________________________________________________________________________
## 11. Wilcoxon tests (12 tests- 6 for crawlers comparing high vs. low pair scores and 6 for non-crawlers)

Summary stats for non-crawlers on perctF_FA (chose this one from above graph)
```{r}
group_by(non_crawlersMANOVA, HighLowEEscore) %>%
  summarise(
    count = n(),
    median = median(perctF_FA, na.rm = TRUE),
    IQR = IQR(perctF_FA, na.rm = TRUE)
  )
```

Boxplots (chosen from above graph)
```{r}
ggplot(non_crawlersMANOVA, aes(x = HighLowEEscore, y = perctF_FA, fill = HighLowEEscore)) +
  geom_boxplot()
```

Wilcoxon (two-sample)
```{r}
wilres <- wilcox.test(perctF_FA ~ HighLowEEscore, data = non_crawlersMANOVA, exact = FALSE)
wilres
```

Summary stats for crawlers on perctA_AN, perctH_AH, and perctN_HN (chose these from above graph)
```{r}
group_by(crawlersMANOVA, HighLowEEscore) %>%
  summarise(
    count = n(),
    median = median(perctA_AN, na.rm = TRUE),
    IQR = IQR(perctA_AN, na.rm = TRUE)
  )
```

Wilcoxon one-sample- non-crawlers, comparing low EE and high EE scorers on perctF_FA to chance 
```{r}

non_crawlersMANOVAlow <- non_crawlersMANOVA %>%
  filter(HighLowEEscore == "low")
non_crawlersMANOVAhigh <- non_crawlersMANOVA %>%
  filter(HighLowEEscore == "high")

reswilone <- wilcox.test(non_crawlersMANOVAlow$perctF_FA, mu = .50)
reswilone2 <- wilcox.test(non_crawlersMANOVAhigh$perctF_FA, mu = .50)

reswilone
reswilone2
```

Wilcoxon one-sample- crawlers, comparing low EE and high EE scorers on perctA_AN, perctH_AH, perctN_HN to chance
```{r}
crawlersMANOVAlow <- crawlersMANOVA %>%
  filter(HighLowEEscore == "low")
crawlersMANOVAhigh <- crawlersMANOVA %>%
  filter(HighLowEEscore == "high")

reswilone3 <- wilcox.test(crawlersMANOVAlow$perctA_AN, mu = .50)
reswilone4 <- wilcox.test(crawlersMANOVAhigh$perctA_AN, mu = .50)

reswilone5 <- wilcox.test(crawlersMANOVAlow$perctH_AH, mu = .50)
reswilone6 <- wilcox.test(crawlersMANOVAhigh$perctH_AH, mu = .50)

reswilone7 <- wilcox.test(crawlersMANOVAlow$perctN_HN, mu = .50)
reswilone8 <- wilcox.test(crawlersMANOVAhigh$perctN_HN, mu = .50)

reswilone3
reswilone4
reswilone5
reswilone6
reswilone7
reswilone8
```

