---
title: "EP analyses"
output: html_notebook
---

## 1. Mean look time per facial expression for each crawling group and data viz
## 2. One sample t-tests (A/H, F/A, H/N, H/F, N/F, A/N)
## 3. 2 X 4 mixed model ANOVA


_________________________________________________________________________________________________
Set WD
```{r}
setwd("~/MATLAB")
```

Libraries
```{r}
library(readxl)
library(formattable)
library(tidyverse)
library(car)
library(apaTables)
library(jtools)

```

Getting data
```{r}
EPAR_full <- read_excel("EP SPSS (N = 56) 8.22.xlsx")
```

_____________________________________________________________________________________________
## 1. Mean look time per facial expression for each crawling group
```{r}
avg_LT <- EPAR_full %>%
  select(CrawlingYN, avgperctH_AH, avgperctA_AH, avgperctF_FA, avgperctA_FA, avgperctH_HN, avgperctN_HN, avgperctH_HF, avgperctF_HF, avgperctN_NF, avgperctF_NF, avgperctA_AN, avgperctN_AN) %>%
  group_by(CrawlingYN) %>%
  summarize(meanH_AH = mean(avgperctH_AH, na.rm = TRUE),
            meanA_AH = mean(avgperctA_AH, na.rm = TRUE),
            meanF_FA = mean(avgperctF_FA, na.rm = TRUE),
            meanA_FA = mean(avgperctA_FA, na.rm = TRUE),
            meanH_HN = mean(avgperctH_HN, na.rm = TRUE),
            meanN_HN = mean(avgperctN_HN, na.rm = TRUE),
            meanH_HF = mean(avgperctH_HF, na.rm = TRUE),
            meanF_HF = mean(avgperctF_HF, na.rm = TRUE),
            meanN_NF = mean(avgperctN_NF, na.rm = TRUE),
            meanF_NF = mean(avgperctF_NF, na.rm = TRUE),
            meanA_AN = mean(avgperctA_AN, na.rm = TRUE),
            meanN_AN = mean(avgperctN_AN, na.rm = TRUE)
            )
avg_LT
```

Reshaping the above table for graphing purposes
```{r}
means_EPAR <- avg_LT %>% 
  gather(Expression, Proportion, meanH_AH:meanN_AN)
means_EPAR
```

Add pair column
```{r}
Pairs <- c("AH", "AH", "AH", "AH", "FA", "FA", "FA", "FA", "HN", "HN", "HN", "HN", "HF", "HF", "HF", "HF", "NF", "NF", "NF", "NF", "AN", "AN", "AN", "AN")

means_EPAR <- cbind(means_EPAR, Pairs)
```

Bar graph of mean total look time to certain face in each expression pair based on crawling status
```{r}

means_EPAR$CrawlingYN <- factor(means_EPAR$CrawlingYN, levels = c("0", "1"), 
                  labels = c("Pre-Crawlers", "Experienced Crawlers"))


means_EPAR$Expression <- factor(means_EPAR$Expression, levels = c("meanH_AH", "meanA_AH", "meanF_FA", "meanA_FA", "meanH_HN", "meanN_HN", "meanH_HF", "meanF_HF", "meanN_NF", "meanF_NF", "meanA_AN", "meanN_AN"), 
                  labels = c("Happy", "Angry", "Fear", "Angry", "Happy", "Neutral", "Happy", "Fear", "Neutral", "Fear", "Angry", "Neutral"))

asterisks2 <- data.frame(Pair = c("FA", "HF", "FA", "NF"),
                        Percentage = c(.62, .62, .63, .58),
                        CrawlingYN = c("Pre-Crawlers", "Pre-Crawlers", "Experienced Crawlers",                         "Experienced Crawlers"))

ggplot(means_EPAR, aes(x = factor(Pairs), y = Proportion, fill = factor(Expression))) +
  geom_bar(position = "dodge", stat = "identity") +
  facet_grid(. ~ CrawlingYN) +
  coord_cartesian(ylim = c(0.3, 0.7)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", size = 0.5) +
  xlab("Expression Pairs") +
  ylab("Proportion of Look Time") +
  theme_apa(legend.pos = "right", legend.use.title = FALSE,
  legend.font.size = 10, x.font.size = 12, y.font.size = 12,
  facet.title.size = 10, remove.y.gridlines = TRUE,
  remove.x.gridlines = TRUE) +
  theme(legend.key.size = unit(0.5, "cm"),
  legend.key.width = unit(0.5,"cm"))

```

___________________________________________________________________________________________________

## 2. One sample t-tests (A/H, F/A, H/N, H/F, N/F, A/N)

Crawlers
```{r}
# Splitting main dataframe into crawlers and non-crawlers
crawlers <- EPAR_full %>% 
  filter(CrawlingYN == 1)

non_crawlers <- EPAR_full %>%
  filter(CrawlingYN == 0)

# Normality test - crawlers
shapiro.test(crawlers$avgperctA_AH)
shapiro.test(crawlers$avgperctA_AN)
shapiro.test(crawlers$avgperctF_FA)
shapiro.test(crawlers$avgperctN_HN)
shapiro.test(crawlers$avgperctF_NF)
shapiro.test(crawlers$avgperctF_HF)

# Crawlers t-tests
resultA_AH_C <- t.test(crawlers$avgperctA_AH, mu = 0.50)
resultA_AN_C <- t.test(crawlers$avgperctA_AN, mu = 0.50)
resultF_FA_C <- t.test(crawlers$avgperctF_FA, mu = 0.50)
resultF_HF_C <- t.test(crawlers$avgperctF_HF, mu = 0.50)
resultN_HN_C <- t.test(crawlers$avgperctN_HN, mu = 0.50)
resultF_NF_C <- t.test(crawlers$avgperctF_NF, mu = 0.50)

resultA_AH_C
resultA_AN_C
resultF_FA_C
resultF_HF_C
resultN_HN_C
resultF_NF_C

```


Bar graph for crawlers (have to change where asterisks are based on above significance)
```{r}
avg_percts_C <- crawlers %>%
  select(avgperctA_AH, avgperctA_AN, avgperctF_FA, avgperctF_HF, avgperctF_NF, avgperctN_HN) %>%
  summarize(mean_perctA_AHC = mean(avgperctA_AH, na.rm = TRUE),
            mean_perctA_ANC = mean(avgperctA_AN, na.rm = TRUE),
            mean_perctF_FAC = mean(avgperctF_FA, na.rm = TRUE),
            mean_perctF_HFC = mean(avgperctF_HF, na.rm = TRUE),
            mean_perctF_NFC = mean(avgperctF_NF, na.rm = TRUE),
            mean_perctN_HNC = mean (avgperctN_HN, na.rm = TRUE))

means_crawlers_prop <- avg_percts_C %>% 
  gather(Pair, Proportion, mean_perctA_AHC:mean_perctN_HNC)

asterisks <- data.frame(Pair = c("mean_perctF_FAC", "mean_perctF_NFC"),
                        Percentage = c(.63, .58))

C_bargraph <- ggplot(means_crawlers_prop, aes(x = factor(Pair), y = Proportion)) +
  geom_bar(position = "dodge", stat = "identity") +
  coord_cartesian(ylim = c(0.3, 0.7)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", size = 0.5) +
  geom_text(data = asterisks, label = "*", size = 10)
C_bargraph
```

Non-crawlers
```{r}
# Normality test - NC
shapiro.test(non_crawlers$avgperctA_AH)
shapiro.test(non_crawlers$avgperctA_AN)
shapiro.test(non_crawlers$avgperctF_FA)
shapiro.test(non_crawlers$avgperctN_HN)
shapiro.test(non_crawlers$avgperctF_NF)
shapiro.test(non_crawlers$avgperctF_HF)

# NC t-tests
resultA_AH_NC <- t.test(non_crawlers$avgperctA_AH, mu = 0.50)
resultA_AN_NC <- t.test(non_crawlers$avgperctA_AN, mu = 0.50)
resultF_FA_NC <- t.test(non_crawlers$avgperctF_FA, mu = 0.50)
resultF_HF_NC <- t.test(non_crawlers$avgperctF_HF, mu = 0.50)
resultN_HN_NC <- t.test(non_crawlers$avgperctN_HN, mu = 0.50)
resultF_NF_NC <- t.test(non_crawlers$avgperctF_NF, mu = 0.50)

resultA_AH_NC
resultA_AN_NC
resultF_FA_NC
resultF_HF_NC
resultN_HN_NC
resultF_NF_NC

```

Bar graph for non_crawlers (have to change where asterisks are based on above significance)
```{r}
avg_percts_NC <- crawlers %>%
  select(avgperctA_AH, avgperctA_AN, avgperctF_FA, avgperctF_HF, avgperctF_NF, avgperctN_HN) %>%
  summarize(mean_perctA_AHNC = mean(avgperctA_AH, na.rm = TRUE),
            mean_perctA_ANNC = mean(avgperctA_AN, na.rm = TRUE),
            mean_perctF_FANC = mean(avgperctF_FA, na.rm = TRUE),
            mean_perctF_HFNC = mean(avgperctF_HF, na.rm = TRUE),
            mean_perctF_NFNC = mean(avgperctF_NF, na.rm = TRUE),
            mean_perctN_HNNC = mean (avgperctN_HN, na.rm = TRUE))

means_non_crawlers_prop <- avg_percts_NC %>% 
  gather(Pair, Proportion, mean_perctA_AHNC:mean_perctN_HNNC)

asterisks <- data.frame(Pair = c("mean_perctF_FANC", "mean_perctF_HFNC"),
                        Percentage = c(.61, .61))

NC_bar <- ggplot(means_non_crawlers_prop, aes(x = factor(Pair), y = Proportion)) +
  geom_bar(position = "dodge", stat = "identity") +
  coord_cartesian(ylim = c(0.3, 0.7)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", size = 0.5) +
  geom_text(data = asterisks, label = "*", size = 10)
NC_bar
```
________________________________________________________________________________________
## 3. 2 (crawling status: experienced crawlers, pre-crawlers) x 4 (expression: fearful. angry, happy, neutral) mixed model ANOVA 

```{r}
EPAR_ANOVA <- EPAR_full %>%
  select(CrawlingYN, avgTLTHappy, avgTLTFear, avgTLTAngry, avgTLTNeutral)

EPAR_ANOVA_long <- EPAR_ANOVA %>% 
  gather(Expression, TLT, avgTLTHappy:avgTLTNeutral)

EPAR_ANOVA_long$Expression <- as.factor(EPAR_ANOVA_long$Expression)
EPAR_ANOVA_long$CrawlingYN <- as.factor(EPAR_ANOVA_long$CrawlingYN)

levels(EPAR_ANOVA_long$Expression) <- list("Happy" = "avgTLTHappy", "Fear" = "avgTLTFear", "Angry" = "avgTLTAngry", "Neutral" = "avgTLTNeutral")
levels(EPAR_ANOVA_long$CrawlingYN) <- list("Non-Crawler" = 0, "Crawler"= 1)

options(contrasts = c("contr.helmert", "contr.poly"))

my_EPAR_anova <- aov(TLT ~ CrawlingYN * Expression, data = EPAR_ANOVA_long)
Anova(my_EPAR_anova, type = "III")
```

```{r}
EPAR_bar <- EPAR_ANOVA %>%
  summarize(mean_Happy = mean(avgTLTHappy, na.rm = TRUE),
            mean_Fear = mean(avgTLTFear, na.rm = TRUE),
            mean_Neutral = mean(avgTLTNeutral, na.rm = TRUE),
            mean_Angry = mean(avgTLTAngry, na.rm = TRUE),
            sd_Happy = sd(avgTLTHappy),
            sd_Fear = sd(avgTLTFear),
            sd_Neutral = sd(avgTLTNeutral),
            sd_Angry = sd(avgTLTAngry),
            se_Happy = sd_Happy/sqrt(56),
            se_Fear = sd_Fear/sqrt(56),
            se_Neutral = sd_Neutral/sqrt(56),
            se_Angry = sd_Angry/sqrt(56))

EPAR_bar_long <- EPAR_bar %>% 
  gather(Expression, TLT, mean_Happy:mean_Angry)

##can i change "identity" and create the mean that way so I can have error bars? or can i manually insert the error bars like the asterisks?

ANOVA_bar <- ggplot(EPAR_bar_long, aes(x = factor(Expression), y = TLT, fill = factor(Expression))) +
  geom_bar(position = "dodge", stat = "identity") +
  theme_apa(legend.pos = "right", legend.use.title = FALSE,
  legend.font.size = 12, x.font.size = 12, y.font.size = 12,
  facet.title.size = 12, remove.y.gridlines = TRUE,
  remove.x.gridlines = TRUE)
      
      #geom_errorbar(aes(ymin= TLT - , ymax=len+sd), width=.2,
                # position=position_dodge(.9)) 

ANOVA_bar

```

