---
title: "EPAR VPC coding"
output: html_notebook
---

~~Kate Dixon, 2018~~

Code takes a csv file of hand-coded (using Datavyu), frame-by-frame left/right looks and transforms it into a final data file that has total look time to each stimuli pair and look time to each stimulus within that pair. 

## Set working directory
```{r}
setwd("C:/Users/Kate/Desktop/VPC")
```

## Load packages
```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(plyr)
library(readxl)
```

## Load data- CHANGE NAME OF FILE HERE
```{r load-data}
df <- read.csv("238338 VPC test.csv", header=TRUE)

cell_orders <- read_excel("VPC cell orders.xlsx")
```

## Create new duration variables for individual left and right looks
```{r}
df <- df %>% 
  mutate(LeftLookDuration = LeftLook.offset - LeftLook.onset)

df <- df %>% 
  mutate(RightLookDuration = RightLook.offset - RightLook.onset)
```

## Making a new dataframe for the combined look times
```{r}
total_look_timeXtrial <- data.frame(matrix(vector(), 0, 2))
```

## Combining all left/right look durations for each test trial (i.e., TT1, TT2...)
```{r}
left_look_timeXtrial <- ddply(df, .(LeftLook.code01), numcolwise(sum))
right_look_timeXtrial <- ddply(df, .(RightLook.code01), numcolwise(sum))

left_look_timeXtrial <-left_look_timeXtrial$LeftLookDuration
right_look_timeXtrial <- right_look_timeXtrial$RightLookDuration

left_look_timeXtrial <- as.data.frame(left_look_timeXtrial)
right_look_timeXtrial <- as.data.frame(right_look_timeXtrial)
```

## Total left and right look times per trial
```{r}
left_look_timeXtrial <- slice(left_look_timeXtrial, 1:12)
right_look_timeXtrial <- slice(right_look_timeXtrial, 1:12)
total_look_timeXtrial <- cbind(left_look_timeXtrial,right_look_timeXtrial)
```

## Adding cell order information to total look time- CHANGE CELL NUMBER HERE
```{r}
total_look_timeXtrial <- cbind(total_look_timeXtrial, cell_orders$`Cell 5`)
```

## Calculating total look time per trial
```{r}
total_look_timeXtrial <- total_look_timeXtrial %>% 
  mutate(TotalLT = left_look_timeXtrial + right_look_timeXtrial)
```

## Total look time based on stimuli into six separate dataframes
```{r}
# Rename columns
names(total_look_timeXtrial) <- c("LLXtrial", "RLXtrial", "Stimuli", "TotalLT")

AH_HA <- total_look_timeXtrial[total_look_timeXtrial$Stimuli == "A/H" | total_look_timeXtrial$Stimuli == "H/A",]

FA_AF <- total_look_timeXtrial[total_look_timeXtrial$Stimuli == "F/A" | total_look_timeXtrial$Stimuli == "A/F",]

NH_HN <- total_look_timeXtrial[total_look_timeXtrial$Stimuli == "N/H" | total_look_timeXtrial$Stimuli == "H/N",]

HF_FH <- total_look_timeXtrial[total_look_timeXtrial$Stimuli == "H/F" | total_look_timeXtrial$Stimuli == "F/H",]

NF_FN <- total_look_timeXtrial[total_look_timeXtrial$Stimuli == "N/F" | total_look_timeXtrial$Stimuli == "F/N",]

AN_NA <- total_look_timeXtrial[total_look_timeXtrial$Stimuli == "A/N" | total_look_timeXtrial$Stimuli == "N/A",]
```


## Creating an empty data frame for the finished data
```{r}
final_data <- data.frame(matrix(vector(), 1, 30))
names(final_data) <- c("TLT_AH/HA", "LT2H_A/H", "LT2A_A/H", "perctH_A/H", "perctA_A/H", "TLT_FA/AF", "LT2F_F/A", "LT2A_F/A", "perctF_F/A", "perctA_F/A", "TLT_HN/NH",	"LT2H_H/N",	"LT2N_H/N",	"perctH_H/N", "perctN_H/N", "TLT_HF/FH", "LT2H_H/F", "LT2F_H/F",	"perctH_H/F",	"perctF_H/F", "TLT_NF/FN", "LT2N_N/F", "LT2F_N/F", "perctN_N/F", "perctF_N/F", "TLT_AN/NA", "LT2A_A/N", "LT2N_A/N", "perctA_A/N", "perctN_A/N")

```

## Getting amount of total look time across both trials into final data
```{r}
final_data$`TLT_AH/HA` <- sum(AH_HA$TotalLT)
final_data$`TLT_FA/AF` <- sum(FA_AF$TotalLT)
final_data$`TLT_HN/NH` <- sum(NH_HN$TotalLT)
final_data$`TLT_HF/FH` <- sum(HF_FH$TotalLT)
final_data$`TLT_NF/FN` <- sum(NF_FN$TotalLT)
final_data$`TLT_AN/NA` <- sum(AN_NA$TotalLT)
```

## Finding total look times and proportions of look time to Happy and Angry for A/H trials
```{r}
## Finding total look time to H on A/H trials
H_AH <- data.frame(matrix(vector(), 2, 1))

H_AH <- AH_HA %>%
    filter(Stimuli == "A/H") %>% 
    select(RLXtrial)

H_AH[2] <- AH_HA %>%
    filter(Stimuli == "H/A") %>% 
    select(LLXtrial)

H_AH <- H_AH %>% 
  mutate(totalH_AH = LLXtrial + RLXtrial)

final_data$`LT2H_A/H` <- H_AH$totalH_AH

## Finding total look time to A on A/H trials
final_data$`LT2A_A/H` <- (final_data$`TLT_AH/HA` - final_data$`LT2H_A/H`)

## Finding proportions for A and H on A/H trials
final_data$`perctA_A/H` <- (final_data$`LT2A_A/H` / final_data$`TLT_AH/HA`)
final_data$`perctH_A/H` <- (final_data$`LT2H_A/H` / final_data$`TLT_AH/HA`)

```

## Finding total look times and proportions of look time to Fearful and Angry for F/A trials
```{r}
## Finding total look time to H on A/H trials
F_FA <- data.frame(matrix(vector(), 2, 1))

F_FA <- FA_AF %>%
    filter(Stimuli == "A/F") %>% 
    select(RLXtrial)

F_FA[2] <- FA_AF %>%
    filter(Stimuli == "F/A") %>% 
    select(LLXtrial)

F_FA <- F_FA %>% 
  mutate(totalF_FA = LLXtrial + RLXtrial)

final_data$`LT2F_F/A` <- F_FA$totalF_FA

## Finding total look time to A on F/A trials
final_data$`LT2A_F/A` <- (final_data$`TLT_FA/AF` - final_data$`LT2F_F/A`)

## Finding proportions for F and A on F/A trials
final_data$`perctF_F/A` <- (final_data$`LT2F_F/A` / final_data$`TLT_FA/AF`)
final_data$`perctA_F/A` <- (final_data$`LT2A_F/A` / final_data$`TLT_FA/AF`)
```

## Finding total look times and proportions of look time to Neutral and Happy for N/H trials
```{r}
## Finding total look time to N on N/H trials
N_NH <- data.frame(matrix(vector(), 2, 1))

N_NH <- NH_HN %>%
    filter(Stimuli == "N/H") %>% 
    select(LLXtrial)

N_NH[2] <- NH_HN %>%
    filter(Stimuli == "H/N") %>% 
    select(RLXtrial)

N_NH <- N_NH %>% 
  mutate(totalN_NH = LLXtrial + RLXtrial)

final_data$`LT2N_H/N` <- N_NH$totalN_NH

## Finding total look time to H on N/H trials
final_data$`LT2H_H/N` <- (final_data$`TLT_HN/NH` - final_data$`LT2N_H/N`)

## Finding proportions for F and A on F/A trials
final_data$`perctN_H/N` <- (final_data$`LT2N_H/N` / final_data$`TLT_HN/NH`)
final_data$`perctH_H/N` <- (final_data$`LT2H_H/N` / final_data$`TLT_HN/NH`)
```

## Finding total look times and proportions of look time to Happy and Fearful for H/F trials
```{r}
## Finding total look time to H on H/F trials
H_HF <- data.frame(matrix(vector(), 2, 1))

H_HF <- HF_FH %>%
    filter(Stimuli == "H/F") %>% 
    select(LLXtrial)

H_HF[2] <- HF_FH %>%
    filter(Stimuli == "F/H") %>% 
    select(RLXtrial)

H_HF <- H_HF %>% 
  mutate(totalH_HF = LLXtrial + RLXtrial)

final_data$`LT2H_H/F` <- H_HF$totalH_HF

## Finding total look time to F on H/F trials
final_data$`LT2F_H/F` <- (final_data$`TLT_HF/FH` - final_data$`LT2H_H/F`)

## Finding proportions for F and A on F/A trials
final_data$`perctH_H/F` <- (final_data$`LT2H_H/F` / final_data$`TLT_HF/FH`)
final_data$`perctF_H/F` <- (final_data$`LT2F_H/F` / final_data$`TLT_HF/FH`)
```


## Finding total look times and proportions of look time to Neutral and Fearful for N/F trials
```{r}
## Finding total look time to N on N/F trials
N_NF <- data.frame(matrix(vector(), 2, 1))

N_NF <- NF_FN %>%
    filter(Stimuli == "N/F") %>% 
    select(LLXtrial)

N_NF[2] <- NF_FN %>%
    filter(Stimuli == "F/N") %>% 
    select(RLXtrial)

N_NF <- N_NF %>% 
  mutate(totalN_NF = LLXtrial + RLXtrial)

final_data$`LT2N_N/F` <- N_NF$totalN_NF

## Finding total look time to F on N/F trials
final_data$`LT2F_N/F` <- (final_data$`TLT_NF/FN` - final_data$`LT2N_N/F`)

## Finding proportions for N and F on N/F trials
final_data$`perctN_N/F` <- (final_data$`LT2N_N/F` / final_data$`TLT_NF/FN`)
final_data$`perctF_N/F` <- (final_data$`LT2F_N/F` / final_data$`TLT_NF/FN`)
```

## Finding total look times and proportions of look time to Angry and Neutral for A/N trials
```{r}
## Finding total look time to A on A/N trials
A_AN <- data.frame(matrix(vector(), 2, 1))

A_AN <- AN_NA %>%
    filter(Stimuli == "A/N") %>% 
    select(LLXtrial)

A_AN[2] <- AN_NA %>%
    filter(Stimuli == "N/A") %>% 
    select(RLXtrial)

A_AN <- A_AN %>% 
  mutate(totalA_AN = LLXtrial + RLXtrial)

final_data$`LT2A_A/N` <- A_AN$totalA_AN

## Finding total look time to N on A/N trials
final_data$`LT2N_A/N` <- (final_data$`TLT_AN/NA` - final_data$`LT2A_A/N`)

## Finding proportions for A and N on A/N trials
final_data$`perctA_A/N` <- (final_data$`LT2A_A/N` / final_data$`TLT_AN/NA`)
final_data$`perctN_A/N` <- (final_data$`LT2N_A/N` / final_data$`TLT_AN/NA`)
```

## Writing final data into a csv file- CHANGE NAME OF OUTPUT FILE HERE
```{r}
# Write CSV in R
write.csv(final_data, file = "238338 VPC test final.csv",row.names=FALSE)
```

