---
title: "Right_Order"
output: html_notebook
---

*Kate Dixon 2018*

This is a code intended to take the output of minimum and maximum Affectiva scores for four trials and put them in order for pasting into a master excel file. Output is a file in test trial order (TT1-TT4) and a file in alphabetical order (Angry, Fearful, Happy, Neutral) which matches the order of data columns in the master file.

Could have fixed this in the original Matlab code that cleans the original Affectiva output file...but I like R better.

## Set working directory
```{r}
setwd("C:/Users/Kate/Documents/MATLAB")
```

## Load packages
```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(plyr)
library(readxl)
```

## Load data- *CHANGE NAME OF FILE HERE*
```{r load-data}
minmax4trials <- read_excel("Practice_238355_processedML.xlsx", sheet = "Sheet9")

ARcell_orders <- read_excel("AR cell orders.xlsx")
```

## Getting rid of the range and unecessary columns
```{r}
justminmax <- minmax4trials %>%
      slice(-3) %>%
      slice(-5) %>%
      slice (-7) %>%
      slice (-9) %>%
      select(anger:smirk)
      
```

## Min and Max for TT1 in one row
```{r}
minTT1 <- slice(justminmax, 1)
maxTT1 <- slice(justminmax, 2)

TT1 <- cbind(minTT1,maxTT1)
```

## Min and Max for TT2 in one row
```{r}
minTT2 <- slice(justminmax, 3)
maxTT2 <- slice(justminmax, 4)

TT2 <- cbind(minTT2,maxTT2)
```

## Min and Max for TT3 in one row
```{r}
minTT3 <- slice(justminmax, 5)
maxTT3 <- slice(justminmax, 6)

TT3 <- cbind(minTT3,maxTT3)
```

## Min and Max for TT4 in one row
```{r}
minTT4 <- slice(justminmax, 7)
maxTT4 <- slice(justminmax, 8)

TT4 <- cbind(minTT4,maxTT4)
```

## Writing the min/max Affectiva values for TT1-4 to a csv file *CHANGE NAME OF FILE HERE*
```{r}
the_right_order1 <- cbind(TT1, TT2, TT3, TT4)
write.csv(the_right_order, file = "238355 TT1-TT4.csv")
```

## Adding stimuli order (cell number) to the test trials- *CHANGE CELL NUMBER*
```{r}
the_right_order2 <- rbind(TT1, TT2, TT3, TT4)
the_right_order3 <- cbind(the_right_order2, ARcell_orders$`Cell 6`)
```

## Sorting trials into alphabetical order (A, F, H, N)- *CHANGE CELL NUMBER*
```{r}
the_right_order_alpha <- arrange(the_right_order3,ARcell_orders$`Cell 6`)

the_right_order_alpha2 <- the_right_order_alpha[ -c(61) ]
```

## Getting A,F,H,N trials on one row
```{r}
anger <- slice(the_right_order_alpha2, 1)
fear <- slice(the_right_order_alpha2, 2)
happy <- slice(the_right_order_alpha2, 3)
neutral <- slice(the_right_order_alpha2, 4)

the_right_order_alpha3 <- cbind(anger, fear, happy, neutral)
```

## Writing Affectiva min/max values in set order to csv file *CHANGE NAME OF FILE HERE*
```{r}
write.csv(the_right_order_alpha3, file = "238355 AFHN.csv")
```

