---
title: "Visualizing Affectiva output by trial"
output: html_notebook
---

Change participant # - 12 places
Change cell # - 1 place
Change crawling to 0 or 1 - 4 places

Clear environment
```{r}
remove(list = ls())
```

Set working directory
```{r}
setwd("C:/Users/Kate/Documents/MATLAB")
```

Load packages
```{r load-packages, message = FALSE}
library(tidyverse)
library(readxl)
```

Load data- *CHANGE NAME OF FILE HERE- processed ML file has to be saved as just a workbook or it won't work*
```{r load-data}
Trial_1 <- read_excel("239847_processedML.xlsx", sheet = "Sheet5")
Trial_2 <- read_excel("239847_processedML.xlsx", sheet = "Sheet6")
Trial_3 <- read_excel("239847_processedML.xlsx", sheet = "Sheet7")
Trial_4 <- read_excel("239847_processedML.xlsx", sheet = "Sheet8")

ARcell_orders <- read_excel("AR cell orders.xlsx")
```

Renaming trials to H, A, N, F *CHANGE CELL NUMBER HERE*
```{r}
order <- ARcell_orders$`Cell 10`

assign(order[1], Trial_1)
assign(order[2], Trial_2)
assign(order[3], Trial_3)
assign(order[4], Trial_4)
```

Grabbing only negative AUs and one timing variable (seconds)
```{r}
H_negAUs <- H %>%
      select(original_fileTimes, inner_brow_raise, brow_raise, brow_furrow, nose_wrinkle, upper_lip_raise, lip_corner_depressor, chin_raise, lip_stretch, lip_press)
      
F_negAUs <- F %>%
      select(original_fileTimes, inner_brow_raise, brow_raise, brow_furrow, nose_wrinkle, upper_lip_raise, lip_corner_depressor, chin_raise, lip_stretch, lip_press)

A_negAUs <- A %>%
      select(original_fileTimes, inner_brow_raise, brow_raise, brow_furrow, nose_wrinkle, upper_lip_raise, lip_corner_depressor, chin_raise, lip_stretch, lip_press)

N_negAUs <- N %>%
      select(original_fileTimes, inner_brow_raise, brow_raise, brow_furrow, nose_wrinkle, upper_lip_raise, lip_corner_depressor, chin_raise, lip_stretch, lip_press)
```

Adding standardized time variable
```{r}
H_negAUs$Standardized_time <- (H_negAUs$original_fileTimes - (H_negAUs$original_fileTimes[1]))

F_negAUs$Standardized_time <- (F_negAUs$original_fileTimes - (F_negAUs$original_fileTimes[1]))

A_negAUs$Standardized_time <- (A_negAUs$original_fileTimes - (A_negAUs$original_fileTimes[1]))

N_negAUs$Standardized_time <- (N_negAUs$original_fileTimes - (N_negAUs$original_fileTimes[1]))
```


Reshaping data
```{r}
H_negAUs_long <- H_negAUs %>%
      gather(AU, Intensity, inner_brow_raise:lip_press)
F_negAUs_long <- F_negAUs %>%
      gather(AU, Intensity, inner_brow_raise:lip_press)
A_negAUs_long <- A_negAUs %>%
      gather(AU, Intensity, inner_brow_raise:lip_press)
N_negAUs_long <- N_negAUs %>%
      gather(AU, Intensity, inner_brow_raise:lip_press)
```


Visualizing Trial H
```{r}
ggplot(data = H_negAUs_long, aes(x = Standardized_time, y = Intensity, color = AU)) +
      geom_point()
```

Visualizing Trial F
```{r}
ggplot(data = F_negAUs_long, aes(x = Standardized_time, y = Intensity, color = AU)) +
      geom_point()
```

Visualizing Trial A
```{r}
ggplot(data = A_negAUs_long, aes(x = Standardized_time, y = Intensity, color = AU)) +
      geom_point()
```

Visualizing Trial N
```{r}
ggplot(data = N_negAUs_long, aes(x = Standardized_time, y = Intensity, color = AU)) +
      geom_point()
```
*CHANGE PART # HERE* and *CHANGE CRAWLING OR NC*
```{r}
N_negAUs$participant <- 239847
N_negAUs$crawlingYN <- 0

H_negAUs$participant <- 239847
H_negAUs$crawlingYN <- 0

A_negAUs$participant <- 239847
A_negAUs$crawlingYN <- 0

F_negAUs$participant <- 239847
F_negAUs$crawlingYN <- 0

```

Write to CSV (4 files, one for each trial) *CHANGE PART # HERE*
```{r}
write.csv(N_negAUs, file = "239847 neutral negAUs.csv")
write.csv(H_negAUs, file = "239847 happy negAUs.csv")
write.csv(A_negAUs, file = "239847 angry negAUs.csv")
write.csv(F_negAUs, file = "239847 fearful negAUs.csv")
```