---
title: "Visualizing Affectiva output by trial_POS AU"
output: html_notebook
---

Change participant # - 12 places
Change cell # - 1 place
Change crawling to 0 or 1 - 4 places

Clear environment
```{r}
remove(list = ls())
```

Set working directory
```{r}
setwd("C:/Users/Kate/Documents/MATLAB")
```

Load packages
```{r load-packages, message = FALSE}
library(tidyverse)
library(readxl)
```

Load data- *CHANGE NAME OF FILE HERE- processed ML file has to be saved as just a workbook or it won't work*
```{r load-data}
Trial_1 <- read_excel("241111_processedML.xlsx", sheet = "Sheet5")
Trial_2 <- read_excel("241111_processedML.xlsx", sheet = "Sheet6")
Trial_3 <- read_excel("241111_processedML.xlsx", sheet = "Sheet7")
Trial_4 <- read_excel("241111_processedML.xlsx", sheet = "Sheet8")

ARcell_orders <- read_excel("AR cell orders.xlsx")
```

Renaming trials to H, A, N, F *CHANGE CELL NUMBER HERE*
```{r}
order <- ARcell_orders$`Cell 18`

assign(order[1], Trial_1)
assign(order[2], Trial_2)
assign(order[3], Trial_3)
assign(order[4], Trial_4)
```

Grabbing only positive AU and one timing variable (seconds)
```{r}
H_posAU <- H %>%
      select(original_fileTimes, cheek_raise)
      
F_posAU <- F %>%
      select(original_fileTimes, cheek_raise)

A_posAU <- A %>%
      select(original_fileTimes, cheek_raise)

N_posAU <- N %>%
      select(original_fileTimes, cheek_raise)
```

Adding standardized time variable
```{r}
H_posAU$Standardized_time <- (H_posAU$original_fileTimes - (H_posAU$original_fileTimes[1]))

F_posAU$Standardized_time <- (F_posAU$original_fileTimes - (F_posAU$original_fileTimes[1]))

A_posAU$Standardized_time <- (A_posAU$original_fileTimes - (A_posAU$original_fileTimes[1]))

N_posAU$Standardized_time <- (N_posAU$original_fileTimes - (N_posAU$original_fileTimes[1]))
```


Reshaping data
```{r}
H_posAU_long <- H_posAU %>%
      gather(AU, Intensity, cheek_raise)
F_posAU_long <- F_posAU %>%
      gather(AU, Intensity, cheek_raise)
A_posAU_long <- A_posAU %>%
      gather(AU, Intensity, cheek_raise)
N_posAU_long <- N_posAU %>%
      gather(AU, Intensity, cheek_raise)
```


*CHANGE PART # HERE* and *CHANGE CRAWLING OR NC*
```{r}
N_posAU$participant <- 241111
N_posAU$crawlingYN <- 1

H_posAU$participant <- 241111
H_posAU$crawlingYN <- 1

A_posAU$participant <- 241111
A_posAU$crawlingYN <- 1

F_posAU$participant <- 241111
F_posAU$crawlingYN <- 1

```

Write to CSV (4 files, one for each trial) *CHANGE PART # HERE*
```{r}
write.csv(N_posAU, file = "241111 neutral posAU.csv")
write.csv(H_posAU, file = "241111 happy posAU.csv")
write.csv(A_posAU, file = "241111 angry posAU.csv")
write.csv(F_posAU, file = "241111 fearful posAU.csv")
```